### 2018-08-10 scripts/README.Rmd

```{r setup, echo = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, error = FALSE, echo = FALSE)
```

@@

scripts %>% filter(
  level == 1
) %>%
  arrange(ix) %>%
  mutate(
    name = str_glue("[{id}](https://github.com/dynverse/dynbenchmark/tree/master/{location})"),
    order = ifelse(is.na(ix), "", ix)
  ) %>%
  select(order, subfolder = name, description = title) %>%
  knitr::kable()

```

>>>>

```{r echo = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, error = FALSE, echo = FALSE)
```

@@

scripts %>% filter(
  level == 1
) %>%
  arrange(ix) %>%
  mutate(
    name = str_glue("[{id}](https://github.com/dynverse/dynbenchmark/tree/master/{location})"),
    order = ifelse(is.na(ix), "", ix)
  ) %>%
  select(order, subfolder = name, description = title) %>%
  knitr::kable()
```
